Novel lattice Boltzmann method for simulation of strongly shear thinning viscoelastic fluids

### 2024-03-05 NovelLBM.tex
note

The PTT model is specified by a differential equation for the polymer stress $\ma{\tau}$:
	\begin{equation}
		\overset{\nabla}{\ma{\tau}} = -\xi\left(\ma{\tau}\cdot\ma{D} + \ma{D}\cdot\ma{\tau}\right) - e^{\frac{\epsilon\lambda}{\eta_\text{p}}\Tr\ma{\tau}}\frac{\ma{\tau}}{\lambda} + 2\frac{\eta_\text{p}}{\lambda}\ma{D}
		\label{eq:polymerStress}
	\end{equation}
where $\ma{D}$ is the strain rate tensor.
We note that extended forms of the PTT model with a Mittag-Leffler instead of an exponential function have been studied as well \cite{ferras2019}\todo{not really what we want to say here. We took this formula mostly from there}.
The polymer viscosity is denoted $\eta_\text{p}$ and $\lambda$ is the corresponding relaxation time.
$\epsilon$ is the so-called extensibility parameter which controls at what shear rates thinning takes place and $\xi$ describes the slip in the polymer network which we will set to zero in the following.
The upper convected derivative of an arbitrary tensor $\ma{A}$ is defined as follows:
	\begin{equation}
		\overset{\nabla}{\ma{A}} = \frac{\Dif\ma{A}}{\Dif t} - \left(\left(\nabla\vec{u}\right)^\mathrm{T}\cdot\ma{A} + \ma{A}\cdot\left(\nabla\vec{u}\right)\right)
	\end{equation}
where $\vec{u}$ is the fluid velocity and $\left(\nabla\vec{u}\right)_{ij} = \nabla_i\vec{u}_j$.
The material derivative is
	\begin{equation}
		\frac{\Dif\ma{A}}{\Dif t} = \frac{\partial\ma{A}}{\partial t} + \vec{u}\cdot\nabla\ma{A}.
	\end{equation}
Finally, the total fluid stress $\ma{\sigma}$ is the sum of the polymer stress $\ma{\tau}$ and a solvent stress due to the Newtonian solvent with viscosity $\eta_\text{s}$:
	\begin{align}
		\ma{\sigma} &= \ma{\tau} + 2\eta_\text{s}\ma{D} 		\label{eq:totalStress}
	\end{align}

>>>>

The PTT model is specified by a differential equation for the polymer stress $\ma{\tau}$:
	\begin{equation}
		\overset{\nabla}{\ma{\tau}} = -\xi\left(\ma{\tau}\cdot\ma{D} + \ma{D}\cdot\ma{\tau}\right) - e^{\frac{\epsilon\lambda}{\eta_\text{p}}\Tr\ma{\tau}}\frac{\ma{\tau}}{\lambda} + 2\frac{\eta_\text{p}}{\lambda}\ma{D}
		\label{eq:polymerStress}
	\end{equation}
where $\ma{D}$ is the strain rate tensor.
We note that extended forms of the PTT model with a Mittag-Leffler instead of an exponential function have been studied as well \cite{ferras2019}\RK{not really what we want to say here. We took this formula mostly from there}.
The polymer viscosity is denoted $\eta_\text{p}$ and $\lambda$ is the corresponding relaxation time.
$\epsilon$ is the so-called extensibility parameter which controls at what shear rates thinning takes place and $\xi$ describes the slip in the polymer network which we will set to zero in the following.
The upper convected derivative of an arbitrary tensor $\ma{A}$ is defined as follows:
	\begin{equation}
		\overset{\nabla}{\ma{A}} = \frac{\Dif\ma{A}}{\Dif t} - \left(\left(\nabla\vec{u}\right)^\mathrm{T}\cdot\ma{A} + \ma{A}\cdot\left(\nabla\vec{u}\right)\right)
	\end{equation}
where $\vec{u}$ is the fluid velocity and $\left(\nabla\vec{u}\right)_{ij} = \nabla_i\vec{u}_j$.
The material derivative is
	\begin{equation}
		\frac{\Dif\ma{A}}{\Dif t} = \frac{\partial\ma{A}}{\partial t} + \vec{u}\cdot\nabla\ma{A}.
	\end{equation}
Finally, the total fluid stress $\ma{\sigma}$ is the sum of the polymer stress $\ma{\tau}$ and a solvent stress due to the Newtonian solvent with viscosity $\eta_\text{s}$:
	\begin{align}
		\ma{\sigma} &= \ma{\tau} + 2\eta_\text{s}\ma{D} 		\label{eq:totalStress}
	\end{align}
